Residence time, a master variable for a more temporal ecology

### 2015-06-20 paper/Manuscript.Rmd
finishing up Results -KL

---
title: "How residence time constrains diversity"
author: "Ken Locey, Jay Lennon"
date: "May 31, 2015"
setspace: doublespacing
header-includes:
   - \usepackage{array}
output: pdf_document
geometry: margin=2.54cm
---

@@

**P1**—Biological and ecological change is marked by time and from rates of metabolism, growth, and evolution to the duration of seasons, succession, and life history, time is the fundamental dimension of biology. But despite its universal relevance in biological and ecological systems, time is more often used as an independent variable or to characterize rates of change, than it is treated as a primary driver of change and biodiversity. While the large lack of study into the general influence of time is recognized among some ecologists (cite), the precise importance or general influence of time is so rarely mentioned that it may be self-evident, non-existent, or commonly taken for granted. But, this is unlike the influence of other general variables such as space and abundance.

>>>>

---
title: "Residence time, a master variable for a more temporal ecology"
author: "Ken Locey, Jay Lennon"
date: "20 June, 2015"
setspace: doublespacing
header-includes:
   - \usepackage{array}
output: pdf_document
geometry: margin=2.54cm
---

@@

**P1**—Biological processes and ecological change are marked by time. From rates of metabolism, growth, and evolution to the duration of seasons, succession, and life history, time is the central dimension of biology. But despite its universal relevance in biological and ecological systems, time is more often used as an independent variable or to characterize rates of change, than it is treated as a primary driver of change and biodiversity. While the large lack of study into the general influence of time is recognized among some ecologists (cite), the precise importance or general influence of time is so rarely mentioned that it may be self-evident, non-existent, or commonly taken for granted. But, this is unlike the influence of other general variables such as space and abundance.
